### 2020-06-19 magic_paper.tex

We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state. Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment. \ddd{[expand on this -- relate to mana?]}

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.

\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

Resource monotones can now be clearly seen as a special case of covariant resource projections.
\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	State order is covariantly preserved due to the defining property of a monotone, seen in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.

@@

	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$. 
	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the defining monotone condition.

@@

\subsection{Magic, Mana and Majorization}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds. Mana is the basic resource monotone for magic. Here we show that its basic properties are actually special cases of more general majorization features. More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.

@@

\subsection{Mana and Majorization}\label{sec:scmana}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
Mana is the fundamental resource monotone for magic. 
Here we show that its properties are in fact special cases of more general majorization features. 
More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.

>>>>

We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state. Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment. \ddd{[expand on this -- relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - can make plot similar to 4.1 in my thesis}

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

Resource monotones can now be clearly seen as a special case of covariant resource projections.
\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.

@@

	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$. 
	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.

@@

@@

\subsection{Mana and majorization in magic theories}\label{sec:scmana}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
Mana is the fundamental resource monotone for magic. 
Here we show that its properties are in fact special cases of more general majorization features. 
More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
